\section*{Population Growth in Korea: 1700 - 2020}

\subsection*{1700 - 1950 (Every 50 years)}
\begin{itemize}
    \item \textbf{1700}: Estimated to be around 7 million.
    \item \textbf{1750}: Approximately 7.5 million.
    \item \textbf{1800}: Around 9 million.
    \item \textbf{1850}: Close to 11 million.
    \item \textbf{1900}: Approximately 13 million.
    \item \textbf{1950}: Roughly 30 million (combined population of North and South Korea, immediately post-Korean War).
\end{itemize}

\subsection*{Commentary 1700 - 1950}
\begin{itemize}
    \item \textbf{1700-1900}: Gradual population growth with agricultural development and relative stability in the region.
    \item \textbf{1900-1950}: More rapid population growth, despite the turmoil of the Japanese occupation and the Korean War. Population doubled from 1900 to 1950.
\end{itemize}

\subsection*{1950 - 2020 (Every 10 years)}
\begin{itemize}
    \item \textbf{1950}: Approximately 30 million (combined population of North and South Korea).
    \item \textbf{1960}: Around 35 million (South Korea: 25 million, North Korea: 10 million).
    \item \textbf{1970}: Approximately 38 million (South Korea: 31 million, North Korea: 7 million).
    \item \textbf{1980}: Close to 49 million (South Korea: 39 million, North Korea: 10 million).
    \item \textbf{1990}: Approximately 66 million (South Korea: 43 million, North Korea: 23 million).
    \item \textbf{2000}: About 71 million (South Korea: 47 million, North Korea: 24 million).
    \item \textbf{2010}: Roughly 74 million (South Korea: 50 million, North Korea: 24 million).
    \item \textbf{2020}: Estimated to be around 77 million (South Korea: 51 million, North Korea: 26 million).
\end{itemize}

\subsection*{Commentary 1950 - 2020}
\begin{itemize}
    \item \textbf{1950-1980}: Rapid recovery and growth in South Korea, while North Korea experienced slower growth.
    \item \textbf{1980-2000}: Continued growth in both nations, with South Korea becoming an economic powerhouse.
    \item \textbf{2000-2020}: Steady population growth in South Korea, with slowing growth rates in North Korea.
\end{itemize}

\subsection*{Overall Commentary}
\begin{itemize}
    \item From 1700 to 2020, Korea experienced significant population growth, from 7 million to 77 million.
    \item The region witnessed steady growth until the 20th century, which saw rapid changes due to colonization, war, and economic development.
    \item The separation of North and South Korea led to divergent demographic paths, with South Korea experiencing rapid growth and development, while North Korea faced challenges and slower growth.
\end{itemize}