\section{Population Growth in Russia: 1700 - 2020}

\subsection*{1700 - 1950 (Every 50 years)}
\begin{itemize}
    \item \textbf{1700}: Estimated to be around 14 million.
    \item \textbf{1750}: Approximately 16 million.
    \item \textbf{1800}: Around 37 million.
    \item \textbf{1850}: Close to 60 million.
    \item \textbf{1900}: Approximately 129 million.
    \item \textbf{1950}: Roughly 101 million (Note: the decrease is due to territorial changes and the impact of World War II).
\end{itemize}

\subsection*{Commentary 1700 - 1950}
\begin{itemize}
    \item \textbf{1700-1800}: Moderate population growth, with expansion and development of new territories.
    \item \textbf{1800-1900}: Rapid population growth due to territorial expansion and natural increase.
    \item \textbf{1900-1950}: Period marked by significant events including the Russian Revolution, World Wars, and territorial changes, leading to fluctuations in population size.
\end{itemize}

\subsection*{1950 - 2020 (Every 10 years)}
\begin{itemize}
    \item \textbf{1950}: Roughly 101 million.
    \item \textbf{1960}: Around 117 million.
    \item \textbf{1970}: Approximately 130 million.
    \item \textbf{1980}: Close to 139 million.
    \item \textbf{1990}: Approximately 148 million.
    \item \textbf{2000}: About 146 million (a slight decrease, reflecting economic challenges and demographic shifts).
    \item \textbf{2010}: Roughly 142 million.
    \item \textbf{2020}: Estimated to be around 146 million.
\end{itemize}

\subsection*{Commentary 1950 - 2020}
\begin{itemize}
    \item \textbf{1950-1990}: Steady population growth, marked by the post-WWII recovery, industrialization, and the Cold War era.
    \item \textbf{1990-2000}: A period of population decline, associated with economic hardship following the dissolution of the Soviet Union, and declining birth rates.
    \item \textbf{2000-2020}: Population remained relatively stable, with slight fluctuations, reflecting government efforts to address demographic challenges and ongoing social and economic changes.
\end{itemize}

\subsection*{Overall Commentary}
\begin{itemize}
    \item From 1700 to 2020, Russia experienced significant fluctuations in population, influenced by territorial changes, wars, industrialization, and political transformations.
    \item The 19th and early 20th centuries were marked by expansion and growth, while the mid-20th century experienced declines and recoveries.
    \item The late 20th and early 21st centuries have been characterized by demographic challenges, stability, and efforts to spur population growth.
\end{itemize}
