\section{Population Growth in South Africa: 1700 - 2020}

\subsection*{1700 - 1950 (Every 50 years)}
\begin{itemize}
    \item \textbf{1700}: Estimated to be around 50,000 (note that this is an approximation and mostly refers to the colonial population).
    \item \textbf{1750}: Approximately 100,000.
    \item \textbf{1800}: Around 200,000.
    \item \textbf{1850}: Close to 300,000.
    \item \textbf{1900}: Approximately 5 million (significant population growth due to the discovery of gold and diamonds, and the inclusion of indigenous populations in census data).
    \item \textbf{1950}: Roughly 12.7 million.
\end{itemize}

\subsection*{Commentary 1700 - 1950}
\begin{itemize}
    \item \textbf{1700-1800}: Population growth was slow, with the area largely inhabited by indigenous peoples and a small number of European colonists.
    \item \textbf{1800-1900}: The population began to grow more significantly, influenced by the influx of settlers and the exploitation of natural resources.
    \item \textbf{1900-1950}: Rapid population growth, influenced by economic opportunities in mining, though this period was also marked by colonization, racial segregation, and the establishment of apartheid in 1948.
\end{itemize}

\subsection*{1950 - 2020 (Every 10 years)}
\begin{itemize}
    \item \textbf{1950}: Roughly 12.7 million.
    \item \textbf{1960}: Around 17.5 million.
    \item \textbf{1970}: Approximately 22.7 million.
    \item \textbf{1980}: Close to 29 million.
    \item \textbf{1990}: Approximately 37 million.
    \item \textbf{2000}: About 44.8 million.
    \item \textbf{2010}: Roughly 50.6 million.
    \item \textbf{2020}: Estimated to be around 59.3 million.
\end{itemize}

\subsection*{Commentary 1950 - 2020}
\begin{itemize}
    \item \textbf{1950-1990}: Rapid population growth continued, despite the oppressive policies of apartheid. The anti-apartheid movement gained momentum, leading to the end of apartheid and the establishment of a democratic government in 1994.
    \item \textbf{1990-2020}: Continued population growth, though at a slower rate. The country has faced challenges including economic inequality, unemployment, and public health issues, but has also made significant progress in terms of political freedom and civil rights.
\end{itemize}

\subsection*{Overall Commentary}
\begin{itemize}
    \item From 1700 to 2020, the population of South Africa experienced significant growth, increasing from around 50,000 to about 59.3 million.
    \item The 19th and early 20th centuries saw rapid population growth and significant social and political change.
    \item The late 20th and early 21st centuries have been marked by the end of apartheid, the establishment of a democratic government, and ongoing challenges and progress in various sectors.
\end{itemize}
